OECD TiVa LMIC GVCs

### 2015-04-21 OECD-TiVa-LMIC-GVCs.Rmd
add trca nrca plot

 ```{r, echo=FALSE}
 # load the data
load("data/gvc_indicators.RData")
load("data/nrca_df.RData")
load("data/country_vars.RData")
load("data/w1995_2008.RData")

>>>>

 ```{r, echo=FALSE}
 # load the data
load("data/gvc_indicators.RData")
load("data/nrca_df.RData")
load("data/country_vars.RData")
load("data/w1995_2008.RData")
load("data/trca.RData")
